Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add preprintfooter
Remove affiliation
Remove a TBD
addint footnote instead of reference.

% These are ignored, unless 'preprint' option specified.
\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{TBD: short description of paper}

@@

\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}
\authorinfo{Simon HENGEL}
           {TBD}
           {sol@typeful.net}
\authorinfo{Markus KLINIK}
           {Elektrobit Automotive GmbH}
           {markus.klinik@elektrobit.com}

@@

GHCi's type defaulting~\cite{ghc-manual} applies to properties.  If a default type is
not suitable, explicit type-signatures can be used:

\begin{quote}
    TBD: @kazu, can you add this to the bib:
    \url{http://www.haskell.org/ghc/docs/7.4.1/html/users_guide/interactive-evaluation.html}
\end{quote}

>>>>

% These are ignored, unless 'preprint' option specified.
\titlebanner{A draft paper to be submitted to Haskell Symposium 2012}
\preprintfooter{BDD in Haskell}

@@

\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}
\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
\authorinfo{Markus KLINIK}
           {Elektrobit Automotive GmbH}
           {markus.klinik@elektrobit.com}

@@

GHCi's type defaulting~\footnote{%
http://www.haskell.org/ghc/docs/7.4.1/html/users\_guide/interactive-evaluation.html} applies to properties.  If a default type is
not suitable, explicit type-signatures can be used:
